---
title: "research"
---
I leverage advanced statistical techniques to uncover insights about auditory and community health.

Here is some of my recent work.

---

# publications
- Zink, M., **Zhen, L.**, McHaney, J., Klara, J., Yurasits, K., Cancel, V., Flemm, O., Mitchell, C., Datta, J., Chandrasekaran, B., Parthasarathy, A. (2025). Increased listening effort and cochlear neural degeneration underlie behavioral deficits in speech perception in noise in normal hearing middle-aged adults. *eLife*, 10.7554/eLife.102823.1. [[access here](https://elifesciences.org/articles/102823)]
- **Zhen, L.** (2025). Task-Irrelevant Perceptual Learning [Doctoral dissertation, University of Pittsburgh]. D-Scholarship\@Pitt Institutional Repository at the University of Pittsburgh. [[access here](https://d-scholarship.pitt.edu/47112/)]
- Goldberg, E., Pratt, S., McNeil, M., Szuminsky, N., DeHaan, K., & **Zhen, L.**. (2025). Development, Reliability and Concurrent Validity of the American Sign Language Version of the Computerized Revised Token Test. *J Speech Lang Hear Res.*, 10.1044/2024_JSLHR-24-00207. [[access here](https://pubmed.ncbi.nlm.nih.gov/39853161/)]
- **Zhen, L.**, & Pratt, S. (2023). Perceptual, procedural, and task learning for an auditory temporal discrimination task. *J. Acoust. Soc. Am.*, 10.1121/10.0017548. [[access here](https://asa.scitation.org/doi/10.1121/10.0017548)]
- Jedlicka, D., & **Zhen, L.** (2023). PTSD is associated with self-perceived hearing handicap: An evaluation of comorbidities in Veterans with normal audiometric thresholds. *J Am Acad Audiol.*, 10.1055/a-2015-8524. [[access here](https://pubmed.ncbi.nlm.nih.gov/36657469/)]
- Roman, A., **Zhen, L.**, & Pratt, S. (2023). Threshold Estimation and Speech Perception Under Hearing Loss Simulation: Examination of the Immersive Hearing Loss and Prosthesis Simulator. *Am. J. Audiol.*, 10.1044/2023_AJA-23-00155. [[access here](https://pubmed.ncbi.nlm.nih.gov/37956704/)]

---

# presentations


## aging & mutli-talker speech intelligiblity
*presented at the Midwest Auditory Research Conference in 2025*

Overt hearing loss is associated with reduced processing of stimulus temporal fine structure cues that are important for hearing in noise. Middle aged adults are understudied in this domain despite them forming the largest group of listeners with hearing complaints and normal audiograms. What are the perceptual consequences of reduced stimulus temporal fine structure encoding with age?

```{r, fig.align='left', out.width = "800px", out.height="550px", echo=FALSE}
knitr::include_graphics("images/zhen_marc2025.pdf")
```

$$\\[1in]$$


## perceptual, procedural, & task learning
*presented at the Acoustical Society of America in 2021*

What information do we learn during auditory training? Much research has focused on learning to detect changes in stimulus characteristics, but improvements also can reflect acquiring general skills and strategies and learning the perceptual judgment specific to the task. The time course for these learning processes overlap, making it difficult to isolate their individual effects.

```{r, fig.align='left', out.width = "800px", out.height="550px", echo=FALSE}
knitr::include_graphics("images/asa2021.pdf")
```

$$\\[1in]$$


## comorbidities & hearing loss in veterans
*presented at the Joint Defense Veterans Audiology Conference in 2021*

More and more veterans returning from Iraq and Afghanistan are complaining of having hearing problems, but their hearing tests are typically normal. Might their comorbidities explain their hearing problems?

<iframe width="560" height="315" src="https://www.youtube.com/embed/JgREjfMw7Uw" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
