---
title: "research"
---
My research is in auditory perceptual learning. I'm interested in how we learn and process the sounds that we hear.

Here is some of my recent work.

---
# perceptual, procedural, & task learning
*presented at ASA 2021*

What information do we learn during auditory training? Much research has focused on learning to detect changes in stimulus characteristics, but improvements also can reflect acquiring general skills and strategies and learning the perceptual judgment specific to the task. The time course for these learning processes overlap, making it difficult to isolate their individual effects.

```{r, fig.align='left', out.width = "800px", out.height="550px", echo=FALSE}
knitr::include_graphics("images/asa2021.pdf")
```

---
# memory & central auditory processing
*presented at JDVAC 2021*

Central auditory processing describes how the brain processes sound beyond the cochlea Some assessment tools for central auditory processing can be especially challenging for veterans at elevated risk for memory deficits related to traumatic brain injuries and/or post-traumatic stress disorder.

```{r, fig.align='left', out.width = "800px", out.height="550px", echo=FALSE}
knitr::include_graphics("images/memorycap_jdvac2021.pdf")
```

---
# comorbidities & hearing loss in veterans
*presented at JDVAC 2021*

More and more veterans returning from Iraq and Afghanistan are complaining of having hearing problems, but their hearing tests are typically normal. Might their comorbidities explain their hearing problems?

<iframe width="560" height="315" src="https://www.youtube.com/embed/JgREjfMw7Uw" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
